A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-19 04_Severity_MetaAnalysis.Rmd
tidy up estimates chunk

```{r logit_estimates}
1 - exp(PMsev_mvPer$b + PMsev_mvPer$b[1])/(1+exp(PMsev_mvPer$b + PMsev_mvPer$b[1]))
logit_estimates <- ifelse(PMsev_mvPer$b == PMsev_mvPer$b[1], PMsev_mvPer$b, PMsev_mvPer$b + PMsev_mvPer$b[1])
1 - inv_logit(logit_estimates)

backtransform <- function(m, input_only = FALSE, intercept) {
   if (input_only == FALSE) {
      intercept <- m$b[1]

      dat <- data.frame(
         estimates = 1 - inv_logit(c(intercept, m$b[-1] + intercept)),
         StdErr = inv_logit(m$se + intercept) - inv_logit(intercept),
         Zval = c(inv_logit(m$z[1]),
                  inv_logit(m$z[-1] + m$z[1]) - inv_logit(m$z[1])),
         Pval = reportP(m$pval, P_prefix = FALSE),
         CI_lb = 1 - c(inv_logit(m$ci.lb[1]), 
                       inv_logit(m$ci.lb[-1] + intercept)),
         CI_ub = 1 - c(inv_logit(m$ci.ub[1]), 
                       inv_logit(m$ci.ub[-1] + intercept)) 
      )
   }
   if (input_only == TRUE) {
      if (missing(intercept))
         stop("'intercept' argument is empty")
     return( inv_logit(m + intercept) - inv_logit(intercept))
   }
   return(dat)
}
backtransform(PMsev_mvPer)
```

>>>>

```{r logit_estimates}
backtransform <- function(m, input_only = FALSE, intercept) {
   if (input_only == FALSE) {
      intercept <- m$b[1]

      dat <- data.frame(
         estimates = 1 - inv_logit(c(intercept, m$b[-1] + intercept)),
         StdErr = inv_logit(m$se + intercept) - inv_logit(intercept),
         Zval = c(inv_logit(m$z[1]),
                  inv_logit(m$z[-1] + m$z[1]) - inv_logit(m$z[1])),
         Pval = reportP(m$pval, P_prefix = FALSE),
         CI_lb = 1 - c(inv_logit(m$ci.lb[1]), 
                       inv_logit(m$ci.lb[-1] + intercept)),
         CI_ub = 1 - c(inv_logit(m$ci.ub[1]), 
                       inv_logit(m$ci.ub[-1] + intercept)), 
         row.names = colnames(m$G)
      )
   }
   if (input_only == TRUE) {
      if (missing(intercept))
         stop("'intercept' argument is empty")
     return( inv_logit(m + intercept) - inv_logit(intercept))
   }
   return(dat)
}

backtransform(PMsev_mvPer)
```
